Borel regularity for ODEs and thimble integrals

### 2023-06-17 exp-resurgence.tex
Work on Borel regularity proofs

Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
\begin{equation}\label{formal solution}
\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
\end{equation}
where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$. Since the roots $\alpha_1, \ldots, \alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.

Classically it has been proved that the formal solutions $\series{\Psi}_j$ \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums $\hat{\Psi}_j$ satisfy the original equation $\mathcal{P}\hat{\Psi}_j=0$ \cite{Ramis?}\textcolor{magenta}{[Check references]}. Therefore, the distinguished frame of formal solutions becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.

@@

\begin{equation}
\hat{P}_j:=P(\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(\zeta_j)+\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]
\end{equation}

@@

Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$. This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$. Of course, there are $n$ different choices for $\omega_b$.
\subsubsection{Frequency}\label{transl-freq}
The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$. At an ordinary point, we can define $z$ simply as the map
\begin{align*}
z \maps T^*B_b & \to \C \\
\lambda\big|_b & \mapsto 1.
\end{align*}
To get a definition that generalizes to branch points, though, it's worth taking a fancier point of view. Recall that $T^*B_b = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$. Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*B_b^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$. When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$. In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$. We define $z$ as the isomorphism
\begin{align*}
z \maps \van_b^n / \van_b^{n+1} & \to \C \\
\zeta_b + \van^{n+1} & \mapsto 1.
\end{align*}

@@

To make sense of this formula, we ask for the following conditions.
\begin{itemize}
\item The base point $b$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\Gamma_b^\theta$.
\item The ray $\Gamma_b^\theta$ avoids the branch points after leaving $b$.
\item The integral converges. We guarantee this by asking for a pair of simpler conditions.
\begin{itemize}
\item With respect to the flat metric, $f$ grows subexponentially along $\Gamma_b^\theta$~\textbf{[define]}, and is locally integrable throughout.
\item The value of $z$ is in the half-plane $H_{-\theta}$ centered around the ray $e^{-i\theta} [0, \infty)$.
\end{itemize}
\end{itemize}
\subsubsection{The Laplace transform over a branch point}
When $b$ is a branch point, we can still use formula~\ref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T^*B_b$, as long as we take care of a few subtleties. Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$. The function $z$ is defined on $T^*B_b^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*B_b$ along the $n$th-power map. This amounts to substituting $w_b^n$ for $z$ in formula~\ref{laplace:int}. The half-plane $z \in H_{-\theta}$ in $T^*B_b^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T^*B_b$. We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
\subsection{The geometry of the Borel transform}
\begin{itemize}
  \item The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$. It's a formal inverse of the $\laplace_{\zeta, 0}$.
  \item Formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$, we can extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
  \begin{itemize}
    \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$. \textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers. [Not quite\ldots figure out how to make this precise.] }
  \end{itemize}
  \item consequently, $\borel_{\zeta_\alpha}$ acts on trans-monomials $e^{z\alpha}\C\llbracket z^{-1}\rrbracket$ and it formally inverts $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. 
\end{itemize}
\subsection{The Laplace transform: analytic version}
\subsubsection{Regularity and decay properties}\label{reg-decay}
%Let $\zeta$ be the standard coordinate on $\C$, and let $z \maps T^*\C \to \C$ be the fiberwise-linear map $d\zeta \mapsto 1$ (see ``The Geometry of the Laplace Transform'' in {\tt draft2}). The Laplace transform in $\zeta$ turns a function $\varphi$ on $\C$ into a function $\laplace_\zeta \varphi$ on $T^*\C$, defined on the cotangent space of $\zeta = \alpha$ by the integral
%\[ \laplace_\zeta \varphi \big|_{\zeta = \alpha} = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta, \]
where $\Gamma_{\zeta, \alpha}$ is the rightward ray starting at $\zeta = \alpha$ (compare {\tt draft2}). \textcolor{magenta}{We'll use the shorthand $\laplace_{\zeta, \alpha} f := \laplace_\zeta f \big|_{\zeta = \alpha}$ throughout this document [but maybe we should get rid of it].}

Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$. A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it's in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$. Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions which are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout. If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined and holomorphic for $\Re(z) > 0$ on the part of $T^*\C$ that lies over $\Gamma_{\zeta, \alpha}$~\cite[\S 5.6]{diverg-resurg-i}.

The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}$ control the asymptotics of $\laplace_{\zeta, \alpha} f$ at the infinite end of $\Gamma_{z, 0}$. Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest. Let $F = \laplace_{\zeta, 0} f$. Equation~1.8 of \cite{laplace-tfm} shows\footnote{The argument cited still works in our generality. For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textcolor{magenta}{(Sternin \& Shatalov)}.} that
\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
More generally, for $\tau > -1$ \textcolor{magenta}{[prove or cite]},
\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \tau}}\right). \]
Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
\subsubsection{Action on integral operators}\label{L-int-op}
When $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm} 
\begin{equation}%%\label{id:L-mult}
\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
\end{equation}
for all integers $n \ge 0$. You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
for all $\lambda \in (0, \infty)$.
\subsubsection{Change of translation chart}\label{translation}
Define a new coordinate $\zeta_\alpha$ on $\C$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
\begin{align*}
\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
\end{align*}
we learn that
\begin{equation}
    \label{change-chart}
    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.
\end{equation}
\subsubsection{Rescaling of translation structure}
Let's rescale the translation structure of $\C$, expanding displacements by a factor of $\mu \in (0, \infty)$. The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure. The corresponding frequency coordinate $x \maps T^*\C \to \C$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$. From the calculation
\begin{align*}
\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
& = \mu\,\laplace_{\zeta, 0} \varphi
\end{align*}
we learn that
\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $\C$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure. We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
\subsection{The geometry of the Borel transform}

The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$. More precisely, $\borel_\zeta$ is a $\C$-linear map 
\begin{align*}
\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
\end{align*}
where $\delta$ is a ``convolution unit'', namely $\phi\ast \delta= \delta\ast \phi= \phi$ (see convolution below \textcolor{magenta}{[add convolution]}).
In general, by linearity,
\begin{align*}
\borel\textcolor{orange}{_\zeta}\big[a_0 + a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_0\delta + a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
\end{align*}

It follows that $\borel_\zeta$ is a formal inverse of the $\laplace_{\zeta, 0}$: let $\varphi=\sum_{n=0}^{\infty}a_n \zeta^n$
\begin{align*}
    \borel_\zeta \laplace_{\zeta}\varphi&=\borel_\zeta \left[\int_{\Gamma_{\zeta,0}}e^{-z\zeta} \varphi d\zeta\right]\\
    &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\Gamma_{\zeta,0}} e^{-z\zeta}\zeta^n d\zeta\right]\\
    &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
    &=\sum_{n=0}^{\infty}a_n \frac{\zeta^n}{n!}
\end{align*}
where in the second step we formally interchange the integral and the sum.

\subsubsection{Action on transseries}

>>>>

Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
\begin{equation}\label{formal solution}
\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
\end{equation}
where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$. Since the roots $-\alpha_1, \ldots, -\alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.

Classically it has been proved that the formal solutions $\series{\Psi}_j$ in \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums $\hat{\Psi}_j$ satisfy the original equation $\mathcal{P}\hat{\Psi}_j=0$ \cite{Ramis?}\textcolor{magenta}{[Check references]}. Therefore, the distinguished frame of formal solutions becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.

@@

\begin{equation}
\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^dR_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
\end{equation}

@@

Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$. This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$. Of course, there are $n$ different choices for $\omega_b$.
\subsubsection{Frequency}\label{transl-freq}
\textcolor{DarkCyan}{[Instead of thinking of $z$ this way, maybe we should think of it as the coordinate on the ``generic cotangent fiber'' over a non-singular point?]} The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$. At an ordinary point, we can define $z$ simply as the map
\begin{align*}
z \maps T^*B_b & \to \C \\
\lambda\big|_b & \mapsto 1.
\end{align*}
To get a definition that generalizes to branch points, though, it's worth taking a fancier point of view. Recall that $T^*B_b = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$. Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*B_b^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$. When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$. In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$. We define $z$ as the isomorphism
\begin{align*}
z \maps \van_b^n / \van_b^{n+1} & \to \C \\
\zeta_b + \van^{n+1} & \mapsto 1.
\end{align*}

@@

To make sense of this formula, we ask for the following conditions.
\begin{itemize}
\item The base point $b$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\Gamma_b^\theta$.
\item The ray $\Gamma_b^\theta$ avoids the branch points after leaving $b$.
\item The integral converges. We guarantee this by asking for a pair of simpler conditions.
\begin{itemize}
\item With respect to the flat metric, $f$ grows subexponentially along $\Gamma_b^\theta$~\textbf{[define]}, and is locally integrable throughout.
\item The value of $z$ is in the half-plane $H_{-\theta}$ centered around the ray $e^{-i\theta} [0, \infty)$.
\end{itemize}
\end{itemize}
\subsubsection{The Laplace transform over a branch point}
When $b$ is a branch point, we can still use formula~\ref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T^*B_b$, as long as we take care of a few subtleties. Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$. The function $z$ is defined on $T^*B_b^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*B_b$ along the $n$th-power map. This amounts to substituting $w_b^n$ for $z$ in formula~\ref{laplace:int}. The half-plane $z \in H_{-\theta}$ in $T^*B_b^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T^*B_b$. We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
\color{gray}
\subsection{The geometry of the Borel transform}
\begin{itemize}
  \item The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$. It's a formal inverse of the $\laplace_{\zeta, 0}$.
  \item Formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$, we can extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
  \begin{itemize}
    \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$. \textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers. [Not quite\ldots figure out how to make this precise.] }
  \end{itemize}
  \item consequently, $\borel_{\zeta_\alpha}$ acts on trans-monomials $e^{z\alpha}\C\llbracket z^{-1}\rrbracket$ and it formally inverts $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. 
\end{itemize}
\color{black}
\subsection{The Laplace transform: analytic version}
\subsubsection{Regularity and decay properties}\label{reg-decay}
%Let $\zeta$ be the standard coordinate on $\C$, and let $z \maps T^*\C \to \C$ be the fiberwise-linear map $d\zeta \mapsto 1$ (see ``The Geometry of the Laplace Transform'' in {\tt draft2}). The Laplace transform in $\zeta$ turns a function $\varphi$ on $\C$ into a function $\laplace_\zeta \varphi$ on $T^*\C$, defined on the cotangent space of $\zeta = \alpha$ by the integral
%\[ \laplace_\zeta \varphi \big|_{\zeta = \alpha} = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta, \]
where $\Gamma_{\zeta, \alpha}$ is the rightward ray starting at $\zeta = \alpha$ (compare {\tt draft2}). \textcolor{magenta}{We'll use the shorthand $\laplace_{\zeta, \alpha} f := \laplace_\zeta f \big|_{\zeta = \alpha}$ throughout this document [but maybe we should get rid of it].}

Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$. A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it's in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$ \textcolor{magenta}{[shall we write in formula?]}. Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions which are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout. If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined and holomorphic for $\Re(z) > 0$ on the part of $T^*\C$ that lies over $\Gamma_{\zeta, \alpha}$~\cite[\S 5.6]{diverg-resurg-i}.

The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}$ control the asymptotics of $\laplace_{\zeta, \alpha} f$ at the infinite end of $\Gamma_{z, 0}$. Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest. Let $F = \laplace_{\zeta, 0} f$. Equation~1.8 of \cite{laplace-tfm} shows\footnote{The argument cited still works in our generality. For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textcolor{magenta}{(Sternin \& Shatalov)}.} that
\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
More generally, for $\tau > -1$ \textcolor{magenta}{[prove or cite]},
\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \tau}}\right). \]
Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}

\subsubsection{Change of translation chart}\label{translation}
Define a new coordinate $\zeta_\alpha$ on $\C$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
\begin{align*}
\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
\end{align*}
we learn that
\begin{equation}
    \label{change-chart}
    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.
\end{equation}
\subsubsection{Rescaling of translation structure}
Let's rescale the translation structure of $\C$, expanding displacements by a factor of $\mu \in (0, \infty)$. The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure. The corresponding frequency coordinate $x \maps T^*\C \to \C$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$. From the calculation
\begin{align*}
\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
& = \mu\,\laplace_{\zeta, 0} \varphi
\end{align*}
we learn that
\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $\C$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure. We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.

\subsubsection{Action on integral operators}\label{L-int-op}
%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
where $p$ is any point on

It obeys the expected semigroup law \textbf{[Lazarevi\'{c}, \S 1.3]}
\begin{align*}
\partial^{\lambda}_{\zeta, \alpha}\,\partial^{\mu}_{\zeta, \alpha} & = \partial^{\lambda+\mu}_{\zeta, \alpha} & \lambda, \mu \in (-\infty, 0),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer \textbf{[Lazarevi\'{c}, equation~35]}.

For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\partial^{n+\alpha}_{x \text{ from } 0}$ are defined by composing $\partial^{\alpha-1}_{x \text{ from } 0}$ with powers of $\tfrac{\partial}{\partial x}$. However, $\partial^{\alpha-1}_{x \text{ from } 0}$ and $\tfrac{\partial}{\partial x}$ don't commute: their commutator is an initial value operator \textbf{[check, clarify]}. Various ordering conventions give various definitions of $\partial^{n+\alpha}_{x \text{ from } 0} f(x)$, which differ by operators that act on the germ of $f$ at zero \textbf{[Lazarevi\'{c}, \S 1.3---original source Podlubny]}. We'll use the {\em Riemann-Liouville} convention.
\begin{definition}
For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\partial^{n+\alpha}_{x \text{ from } 0}$ is defined by
\[ \partial^{n+\alpha}_{x \text{ from } 0} \defeq \left(\tfrac{\partial}{\partial x}\right)^{n+1} \partial^{\alpha-1}_{x \text{ from } 0}. \]
\end{definition}
The symbol $\partial^\mu_{\zeta \text{ from } 0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$. It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.

The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\partial^\lambda_{x \text{ from } 0}\,\partial^{-\lambda}_{x \text{ from } 0}=\text{Id}$ for all $\lambda \in (0, \infty)$. This extends the semigroup law:
\begin{align*}
\partial^{\lambda}_{x \text{ from } 0}\,\partial^{\mu}_{x \text{ from } 0} & = \partial^{\lambda+\mu}_{x \text{ from } 0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
\end{align*}

Each convention for the fractional derivative brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville derivative will be the least annoying for our purposes. Here's what's nice about it.

You can use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
for all $\lambda \in (0, \infty)$. This generalizes the Laplace transform's action on derivatives: when $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}%%\label{id:L-mult}
\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
\end{equation}
for all integers $n \ge 0$.

\color{magenta}
Furthermore, if $\varphi\in\mathcal{E}_{\zeta,\alpha}$, then $\partial_{\zeta,\alpha}^{-\lambda}\varphi\in\mathcal{E}_{\zeta,\alpha}$ and 
\[ \laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi \]
for all $\lambda \in (0, \infty)$, where the operator $\partial_{\zeta,\alpha}^{-\lambda}$ is defined by

\begin{equation}
    \partial_{\zeta,\alpha}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^{\zeta}(\zeta-t)^{\lambda-1} \varphi(t) dt
\end{equation}

Similarly, $\partial_{\zeta_\alpha,0}^{-\lambda}\varphi\in\mathcal{E}_{\zeta_\alpha,0}$ and 
\[ \laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi \]
for all $\lambda \in (0, \infty)$, where the operator $\partial_{\zeta_\alpha,0}^{-\lambda}$ is defined by

\begin{equation}
    \partial_{\zeta_\alpha,0}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_\alpha}(\zeta_\alpha-t)^{\lambda-1} \varphi(t+\alpha) dt
\end{equation}

Notice that the definition of $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ are indeed the same as it follows by a simple change of coordinates $t\to t+\alpha$. However, there is no contradiction as it can be easily verified using the relation \eqref{change-chart}.

We remark that on a translation surface, there is no preferred coordinate chart, hence either $\zeta$ as local coordinate at $\alpha$ or $\zeta_\alpha$ as local coordinate at $0$ are equivalent choices.

%Notice that $z^{-\lambda}$ is a coordinate on different fibres of $T^*B$: $z\in T_0^*B$ in equation $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, while $z\in T^*_\alpha B$ in equation $\laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi$. In fact, as we will see in Section \ref{convolution}, both $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ can be regarded as a convolution product which depends on the fibre.

%We also remark that $\partial_{\zeta,\alpha}^{-\lambda}\varphi=\partial_{\zeta_\alpha,0}^{-\lambda}\varphi$ for every $\varphi\in\mathcal{E}_{\zeta,\alpha}$ (in fact the path $\Gamma_{\zeta,\alpha}$ is equivalent to the path $\Gamma_{\zeta_\alpha,0}$).
